A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/analysis/analysis_stable.Rmd
Typos. Consistency WIP

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR

@@

ast_sizes %>%
  ggplot(aes(x = eval_source_type, y = expr_resolved_nodes, fill = eval_source_type, weight = nb_ev_calls)) +
  geom_violin(trim = FALSE, width=.5)+
  #geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

@@

```{r}
expr_resolved_replaceable <- expr_resolved_monomorphic %>% left_join(eval_calls) %>% mutate(can_replace = map_lgl(expr_resolved,  is_replaceable_str))
```

>>>>

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /home/pierre/Documents/Articles/ISCE2021

@@

ast_sizes %>%
  ggplot(aes(x = eval_source_type, y = expr_resolved_nodes, fill = eval_source_type, weight = nb_ev_calls), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=.5)+
  geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

```{r}
eval_calls %>% semi_join(expr_resolved_polymorphism %>% filter(polym_degree == max(polym_degree)), by ="eval_call_srcref")
```

@@

```{r}
#expr_resolved_replaceable <- expr_resolved_monomorphic %>% left_join(eval_calls) %>% mutate(can_replace = map_lgl(expr_resolved,  is_replaceable_str))
```

### 2020-08-28 inst/paper/main.tex
B
Typos. Consistency WIP

The three other functions are defined using \lstinline|eval|.

@@

\c{expr} is the expression to be evaluated. It is not a string as in javascript. In order to evaluate a string, it should be first parsed using \c(parse(text = str)) to get an expression.

@@

@@

%%\subsection{Consistency}
%%Here we talk about whether the same call site sees the same pattern
%%
%%{\bf Polymorphic may not be the right word.}
%%
%%We look at how \emph{polymorphic} the \c{expr} argument of \eval can be, \ie
%%how many different types of the resolved \c{expr} there are per call sites,
%%in Figure~\ref{fig:polymorphism}. \PercentMonomorphic of the call sites are
%%\emph{monomorphic}.
%%
%%\begin{figure}[!h]
%%	\centering
%%    \includegraphics[width=\columnwidth]{polymorphism}
%%    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
%%\end{figure}
%%
%%\subsection{base}
%%
%%There are 30 functions in \emph{base} that use \eval. Only five of them use \c{parse}, for legitimate reasons, such \c{source} and \c{sys.source} which load a file and then evaluate it, or \c{invokeRestartInteractively} which prompts the user for arguments to restart execution after an error.
%%
%%We endeavored  to write these functions without \eval. \c{match.arg} appears in \MatchArgPercent of the \eval calls. It is used to get the arguments, possibly abbreviated, of a function. With one argument, as \c{match.arg(arg)}, it uses \c{eval} to infer them from a parent function's formal arguments. We can rewrite it using its version with two arguments, \c{match.arg(arg, choices)} where \c{choices} are the possible formal arguments of the function, as shown in Listing~\ref{code:matcharg}.
%%
%%\begin{lstlisting}[caption={Rewriting \c{match.arg} without \eval}, label=code:matcharg]
%%f <- function(type=c("examples", "tests", "vignettes")) {
%%actual_type = match.arg(type)
%%...
%%}
%%
%%f <- function(type=c("examples", "tests", "vignettes")) {
%%actual_type = match.arg(type, choices=c("examples", "tests", "vignettes"))
%%...
%%}
%%\end{lstlisting}

>>>>

The three other functions are defined using \eval.

@@

\c{expr} is the expression to be evaluated. It is not a string as in javascript. In order to evaluate a string, it should be first parsed using \c{parse(text = str)} to get an expression.

@@

\begin{lstlisting}
> eval(2)
[1] 2
> eval(expression(1+2))
[1] 3
> eval(parse(text = "1 + 2"))
[1] 3
\end{lstlisting}

@@

\subsection{Consistency}

We look at how \emph{polymorphic} the \c{expr} argument of \eval can be, \ie
how many different types of the resolved \c{expr} there are per call sites,
in Figure~\ref{fig:polymorphism}. Most of the call sites, \ie \PercentMonomorphic,  are
\emph{consistent}. However, a few ones are \emph{polymorphic}, such as:

\begin{figure}[!h]
	\centering
    \includegraphics[width=\columnwidth]{polymorphism}
    \caption{Number of different types  of \c{expr} per call sites.} \label{fig:polymorphism}
\end{figure}
%
%\subsection{base}
%
%%There are 30 functions in \emph{base} that use \eval. Only five of them use \c{parse}, for legitimate reasons, such \c{source} and \c{sys.source} which load a file and then evaluate it, or \c{invokeRestartInteractively} which prompts the user for arguments to restart execution after an error.
%%
%%We endeavored  to write these functions without \eval. \c{match.arg} appears in \MatchArgPercent of the \eval calls. It is used to get the arguments, possibly abbreviated, of a function. With one argument, as \c{match.arg(arg)}, it uses \c{eval} to infer them from a parent function's formal arguments. We can rewrite it using its version with two arguments, \c{match.arg(arg, choices)} where \c{choices} are the possible formal arguments of the function, as shown in Listing~\ref{code:matcharg}.
%%
%%\begin{lstlisting}[caption={Rewriting \c{match.arg} without \eval}, label=code:matcharg]
%%f <- function(type=c("examples", "tests", "vignettes")) {
%%actual_type = match.arg(type)
%%...
%%}
%%
%%f <- function(type=c("examples", "tests", "vignettes")) {
%%actual_type = match.arg(type, choices=c("examples", "tests", "vignettes"))
%%...
%%}
%%\end{lstlisting}
